Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-05 paper/main.tex
Added verb environment around function names

The Init() function basically sets up the internal state of the function, to
make it ready to start processing real data. The Update() function is used to
provide the actuall data to the hash function. The Final() function should be
called when all necessary data has been gived through Update(), it will then
finish the hash function and provide the digest. The Hash() function basically a wrapper
for doing a call to the three other functions.

HashReturn is an enum representing that an operation either succeded (0) or
went wrong. The BitSequence is a representation of an array of bytefields and
DataLength represents the size in bits of the data provided.

@@

\subsubsection{\ac{SUPERCOP} \ac{API}}
\ac{SUPERCOP} specifies an \ac{API} which all submitted implementations must
conform to\cite{s_supercopapi}. This \ac{API} specifies the naming and
organization of files, and that a submission must include a function
crypto\_hash() which is similar to the function Hash() in the \ac{NIST} \ac{SHA}-3
\ac{API}. The only difference beeing the naming of datatypes and that the
crypto\_hash() function does not need an input of how long the output of the
hash function should be. Instead double or different submissions are used for
different output lengths.

@@

There are two kinds of files in the Tahoe-\ac{LAFS} -- \textbf{immutable} and
\textbf{mutable} files. An immutable file is created exactly once, i.e. it
cannot be modified, and can be read repeatedly. Mutable files can be modified,
and everyone who has access to the \emph{signing key} can make new versions of
the mutable file.
%More text here?

@@

These secure hashes of the shares of a file, are contained within a small
datastructure named the \emph{\ac{CEB}}.

@@

% FIXME: A more descriptive/better chapter title?
%
%A bit more technical description of how we tested the candidates in Tahoe-LAFS
% - Limitations/assumptions
% - Optimized candidates.
% - Error sources.
% The points above should be taken into consideration on each section in this
% chapter.

>>>>

The {\verb Init() } function basically sets up the internal state of the function, to
make it ready to start processing real data. The {\verb Update() } function is used to
provide the actual data to the hash function. The {\verb Final() } function should be
called when all necessary data has been given through {\verb Update() }, it will then
finish the hash function and provide the digest. The Hash() function basically a wrapper
for doing a call to the three other functions.

{\verb HashReturn } is an \emph{enum} representing that an operation either succeeded (0) or
went wrong. The {\verb BitSequence } is a representation of an array of byte fields and
{\verb DataLength } represents the size in bits of the data provided.

@@

\subsubsection{\ac{SUPERCOP} \ac{API}}
\ac{SUPERCOP} specifies an \ac{API} which all submitted implementations must
conform to\cite{s_supercopapi}. This \ac{API} specifies the naming and
organization of files, and that a submission must include a function
{\verb crypto\_hash() } which is similar to the function {\verb Hash() } in the
\ac{NIST} \ac{SHA}-3 \ac{API}. The only difference being the naming of
data types and that the {\verb crypto\_hash() } function does not need an input
of how long the output of the hash function should be. Instead double or
different submissions are used for different output lengths.

@@

There are two kinds of files in the Tahoe-\ac{LAFS} -- \textbf{immutable} and
\textbf{mutable} files. An immutable file is created exactly once, i.e. it
cannot be modified, and can be read repeatedly. Mutable files can be modified,
and everyone who has access to the signing key can make new versions of
the mutable file.
%More text here?

@@

These secure hashes of the shares of a file, are contained within a small
data structure named the \emph{\ac{CEB}}.

@@

%A bit more technical description of how we tested the candidates in Tahoe-LAFS
% - Limitations/assumptions
% - Optimized candidates.
% - Error sources.
% The points above should be taken into consideration on each section in this
% chapter.
